---
title: "Our findings"
author:
  - name: Matthias Felix
    email: matthias.felix@uzh.ch
    affiliation: 11-746-625
  - name: Florian Fischer
    email: florian.fischer2@uzh.ch
    affiliation: 11-611-985
  - name: Catrin Loch
    email: catrin.loch@uzh.ch
    affiliation: 13-718-143

bibliography: sigproc.bib
output: rticles::acm_article
---
test

```{r setup, include=FALSE}
import::from(lmerTest, lmer, anova)
import::from(car, qqPlot)
import::from(multcomp, glht, mcp)
import::from(broom, tidy)
import::from(modelr, add_residuals, gather_residuals)
import::from(ggpubr, theme_pubclean)
library(tidyverse)
```



```{r, echo=FALSE, fig.height=2, fig.cap = "Example figure caption. \\label{fig:fig_example}"}
tibble(x = rnorm(30), y = rnorm(30)) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_pubclean(base_size = 18)
```

In the `{r setup ...}` chunk above (only visible in the source code), we also use `import::from` to selectively import functions from the packages. 
This prevents functions of similar names from crashing with each other.
To use `import::from`, you'll need to install the `import` package.

You may want to selectively hide some code chunks with `echo=FALSE` (Show only output) or `include=FALSE` (Show nothing, but run code)

```{r include=FALSE}
test_value <- 1.23456
format_num <- function(nums, sigdigits = 3) gsub("\\.$", "", formatC(nums, sigdigits, format = "fg", flag="#"))
```
Sometimes, you can easily format the number with decimal points using the `format_num()` provided in code, such as this: `r format_num(test_value)`.
However, at other times (e.g., $p$ < .001), formatting would be easier if you just type in the number.

The footer on the bottom-left of the page is determined in the template. 
Don't bother wrestling with it.

Please remove the instruction sections from your submission.

Change the title of the submission to a short clause that highlight your findings.

## Dataset

Each group will use a unique subset of data from the given dataset. 
Use the following code block (visible in the source code) to set `group_seed` and generate `my_data`  to generate the dataset for your group.

```{r include=FALSE}
matriculation_nos <- c(12345678, 12345678)  # replace 12345678 with matriculation number of each team member

# load the  whole dataset
sim_data <- readRDS("../data/sim_data.RDS")

# set randomization seed
group_seed <- mean(matriculation_nos) %% 28
set.seed(group_seed)

# randomly sample some participants out of the given dataset
my_data <- 
  sim_data %>% 
  filter(Participant %in% sample(as.character(unique(sim_data$Participant)), 15))

# To ensure that your dataset doesn't change, run the code above only once.
# Afterwards, save and load data with the following command
# saveRDS(my_data, file = "../data/my_data.RDS")
# my_data <- readRDS("../data/my_data.RDS")
```


# Effect of input techniques
__RQ1:__ To which extent does the choice of input techniques influence the pointing performance?

Describe your claim, evidence and reasoning.
Make sure to justify your choice of analysis methods.


# Learning effect
__RQ2:__ To which extent does the learning effect influences the pointing performance?


# Conclusion
In this section, you will write about what you learned by drawing from both RQ1 and RQ2


(For grading `group_seed`: (write down the number of your `group_seed` here))



# References



